The fraction of polar aligned circumbinary disks

### 2025-05-06 src/tex/ms.tex
Small edits by RGM

\subsection{Effects of companions}
\RR{
    In this work we have only considered disks orbiting isolated binary systems, however, we can qualitatively extend our results to hierarchical triple star systems as well. There are two such cases to consider: 1) the outer-companion case where third star orbits exterior to the disk, and 2) the inner-companion case, where the disk orbits the tripe-star system. In both the outer \citep[see][]{martin2022,ceppi2023} and inner \citep[see][]{lepp2023,lepp2025} cases, additional conditions are imposed for libration to occur, and $f_\text{polar}$ decreases. The magnitude of these effects is dependent on the geometry of the triple-star system.
}

>>>>

\subsection{Effects of companions}
\RR{
    In this work we have only considered disks orbiting isolated binary star systems. However, we can qualitatively extend our results to hierarchical triple star systems. There are two such cases to consider: 1) the outer-companion case where a third star orbits exterior to the circumbinary disk, and 2) the inner-companion case, where the disk orbits a triple-star system. In both the outer \citep[see][]{martin2022,ceppi2023} and inner \citep[see][]{lepp2023,lepp2025} cases, additional conditions are imposed for libration to occur, and $f_\text{polar}$ decreases. The magnitude of these effects is highly dependent on the geometry of the triple-star system.
}
